Import OLIS spectral data

### 2023-12-07 Code/JazDataImport.Rmd
Change file path

JazSpec <- JazSpec %>% 
  mutate(Filename = str_remove(Filename, pattern = "../Data/RawData/MCEmissionSpectra/")) |>
  separate(col = Filename, into = c("Date", "MultiCulti", "Par", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE)

@@

 saveRDS(JazSpecNest, file.path(DataOut, paste(Project, "MultiCultiSpectra.Rds", sep = "_"), fsep = .Platform$file.sep))

>>>>

JazSpec <- JazSpec %>% 
  mutate(Filename = str_remove(Filename, pattern = DataIn)) |>
  separate(col = Filename, into = c("FP0","Date", "MultiCulti", "Par", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE) %>% 
  select(-FP0)

@@

 saveRDS(JazSpecNest, file.path(DataOut, paste(Project, "JazEmSpectra.Rds", sep = "_"), fsep = .Platform$file.sep))

### 2023-12-07 Code/OlisImportPurCalc.Rmd
Change file path

```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
# library(knitr)
# library(OneR)
library(zoo)
# library(strucchange)
# library(plotly)
# library(dplyr)
# library(magrittr)
# library(googledrive)
# library(googlesheets4)
library(readxl)

library(ggspectra)
library(ggpubr)
library(caret)
```

```{r set colours}
Wavelengths_nm = c(405, 450, 475, 530, 615, 660, 730, "WW")
Colours_nm = c("violet", "darkblue", "dodgerblue", "darkgreen","orange","red","purple", "black")

names(Colours_nm) <- Wavelengths_nm
Colours_nm

@@

MC_Spectra <- readRDS(file = file.path(DataInSpectra, "PICO_MultiCultiSpectra.Rds"))

@@

```{r, Initial Plots}
OlisSpectraMetaData %>%
  ggplot() +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = Colours_nm) +
 # guides(colour = FALSE) +
  labs(y = "Absorbance", x = "Wavelength (nm)") +
  scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
  coord_cartesian(ylim = c (0, 0.2)) +
  ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

OlisSpectraMetaData %>%
   filter(Strain == "MED4",
          ID != "MiSa1289",
          ID != "MiSa1294") %>% 
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Blue_nm, colour = "violet", label = ID)) +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = Colours_nm) +
 # guides(colour = FALSE) +
  labs(subtitle = "Normalized to Max Abs in blue range (400 to 460 nm)", y = "Normalized Absorbance", x = "Wavelength (nm)") +
  #scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
  ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

OlisSpectraMetaData %>%
   filter(Strain == "MED4",
          ID != "MiSa1289",
          ID != "MiSa1294") %>% 
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Red_nm, colour = "violet", label = ID)) +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = Colours_nm) +
  #guides(colour = FALSE) +
 labs(subtitle = "Normalized to Max Abs in red range (575 to 750 nm)", y = "Normalized Absorbance", x = "Wavelength (nm)") +
  # scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
  # coord_cartesian(ylim = c (0, 0.2)) +
 ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

OlisSpectraMetaData %>%
   filter(Strain == "SS120",
          ID != "MiSa1289",
          ID != "MiSa1315") %>% 
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Blue_nm, colour = "violet", label = ID)) +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = Colours_nm) +
 # guides(colour = FALSE) +
  labs(subtitle = "Normalized to Max Abs in blue range (400 to 460 nm)", y = "Normalized Absorbance", x = "Wavelength (nm)") +
  #scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
  ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

OlisSpectraMetaData %>%
   filter(Strain == "SS120",
          ID != "MiSa1289",
          ID != "MiSa1315") %>% 
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Red_nm, colour = "violet", label = ID)) +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = Colours_nm) +
  #guides(colour = FALSE) +
 labs(subtitle = "Normalized to Max Abs in red range (575 to 750 nm)", y = "Normalized Absorbance", x = "Wavelength (nm)") +
  # scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
  # coord_cartesian(ylim = c (0, 0.2)) +
 ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

OlisSpectraMetaData %>%
   filter(Strain == "MIT9313",
          ID != "MiSa1294",
          ID != "MiSa1315") %>% 
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Blue_nm, colour = "violet", label = ID)) +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = Colours_nm) +
 # guides(colour = FALSE) +
  labs(subtitle = "Normalized to Max Abs in blue range (400 to 460 nm)", y = "Normalized Absorbance", x = "Wavelength (nm)") +
  #scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
  ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

OlisSpectraMetaData %>%
   filter(Strain == "MIT9313",
          ID != "MiSa1315",
          ID != "MiSa1294") %>% 
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Red_nm, colour = "violet", label = ID)) +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = Colours_nm) +
  #guides(colour = FALSE) +
 labs(subtitle = "Normalized to Max Abs in red range (575 to 750 nm)", y = "Normalized Absorbance", x = "Wavelength (nm)") +
  # scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
  # coord_cartesian(ylim = c (0, 0.2)) +
 ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

@@

OlisSpectraMetaData %>%
   filter(ID == "MiSa1289" |
          ID == "MiSa1315" |
          ID == "MiSa1294" |
          ID == "MiSa1722" |
          ID == "MiSa1723") %>%
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Blue_nm, colour = (ID))) +
 # geom_point(aes(x = nm, y = Absorbance, colour = ID)) +
 #scale_color_manual(values = Colours_nm) +
  #guides(colour = FALSE) +
 labs(y = "Normalized Absorbance", x = "Wavelength (nm)", size = 20, color = "black" ) +
    scale_y_continuous(breaks = c(0,0.2, 0.4,0.6, 0.8, 1.0, 1.2), limits = c (0, 1.2)) +
   # scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
 scale_color_manual(values = Stock_ID, label = Stock_Label) +
  # coord_cartesian(ylim = c (0, 0.2)) +
 #ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+ 
 theme(
        axis.title = element_text(size = 20, color = "black"),
        axis.text = element_text(size = 15, color = "black"),
        # strip.background=element_rect(color="grey", fill = "grey"),
        # strip.background=element_rect(fill = "grey"),
        # legend.key.size = unit(1, 'cm'), #change legend key size
        # legend.key.height = unit(1, 'cm'), #change legend key height
        # legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title = element_text(size = 15),  #change legend title font size
   legend.text = element_text(size = 15)) + #change legend text font size
  labs(colour = "Strain")

>>>>

```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
# library(knitr)
# library(OneR)
library(zoo)
# library(strucchange)
# library(plotly)
# library(dplyr)
# library(magrittr)
# library(googledrive)
# library(googlesheets4)
library(readxl)
library(photobiologyWavebands)
library(ggspectra)
library(ggpubr)
library(caret)
```

```{r set colours}
MyWavelengths = c(405, 445, 470, 530, 620, 660, 730, "WW")
MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(445), w_length2rgb(470), w_length2rgb(530), 
                   w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black"))

names(MCMIXColours) <- MyWavelengths
MCMIXColours

@@

MC_Spectra <- readRDS(file = file.path(DataInSpectra, "PICO_JazEmSpectra.Rds"))

@@

```{r, Initial Plots}
OlisSpectraMetaData %>%
  ggplot() +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = MCMIXColours) +
 # guides(colour = FALSE) +
  labs(y = "Absorbance", x = "Wavelength (nm)") +
  scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
  coord_cartesian(ylim = c (0, 0.2)) +
  ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

OlisSpectraMetaData %>%
   filter(Strain == "MED4",
          ID != "MiSa1289",
          ID != "MiSa1294") %>% 
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Blue_nm, colour = "violet", label = ID)) +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = MCMIXColours) +
 # guides(colour = FALSE) +
  labs(subtitle = "Normalized to Max Abs in blue range (400 to 460 nm)", y = "Normalized Absorbance", x = "Wavelength (nm)") +
  #scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
  ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

OlisSpectraMetaData %>%
   filter(Strain == "MED4",
          ID != "MiSa1289",
          ID != "MiSa1294") %>% 
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Red_nm, colour = "violet", label = ID)) +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = MCMIXColours) +
  #guides(colour = FALSE) +
 labs(subtitle = "Normalized to Max Abs in red range (575 to 750 nm)", y = "Normalized Absorbance", x = "Wavelength (nm)") +
  # scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
  # coord_cartesian(ylim = c (0, 0.2)) +
 ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

OlisSpectraMetaData %>%
   filter(Strain == "SS120",
          ID != "MiSa1289",
          ID != "MiSa1315") %>% 
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Blue_nm, colour = "violet", label = ID)) +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = MCMIXColours) +
 # guides(colour = FALSE) +
  labs(subtitle = "Normalized to Max Abs in blue range (400 to 460 nm)", y = "Normalized Absorbance", x = "Wavelength (nm)") +
  #scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
  ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

OlisSpectraMetaData %>%
   filter(Strain == "SS120",
          ID != "MiSa1289",
          ID != "MiSa1315") %>% 
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Red_nm, colour = "violet", label = ID)) +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = MCMIXColours) +
  #guides(colour = FALSE) +
 labs(subtitle = "Normalized to Max Abs in red range (575 to 750 nm)", y = "Normalized Absorbance", x = "Wavelength (nm)") +
  # scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
  # coord_cartesian(ylim = c (0, 0.2)) +
 ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

OlisSpectraMetaData %>%
   filter(Strain == "MIT9313",
          ID != "MiSa1294",
          ID != "MiSa1315") %>% 
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Blue_nm, colour = "violet", label = ID)) +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = MCMIXColours) +
 # guides(colour = FALSE) +
  labs(subtitle = "Normalized to Max Abs in blue range (400 to 460 nm)", y = "Normalized Absorbance", x = "Wavelength (nm)") +
  #scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
  ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

OlisSpectraMetaData %>%
   filter(Strain == "MIT9313",
          ID != "MiSa1315",
          ID != "MiSa1294") %>% 
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Red_nm, colour = "violet", label = ID)) +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = MCMIXColours) +
  #guides(colour = FALSE) +
 labs(subtitle = "Normalized to Max Abs in red range (575 to 750 nm)", y = "Normalized Absorbance", x = "Wavelength (nm)") +
  # scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
  # coord_cartesian(ylim = c (0, 0.2)) +
 ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

@@

OlisSpectraMetaData %>%
   filter(ID == "MiSa1289" |
          ID == "MiSa1315" |
          ID == "MiSa1294" |
          ID == "MiSa1722" |
          ID == "MiSa1723") %>%
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Blue_nm, colour = (ID))) +
 # geom_point(aes(x = nm, y = Absorbance, colour = ID)) +
 #scale_color_manual(values = MCMIXColours) +
  #guides(colour = FALSE) +
 labs(y = "Normalized Absorbance", x = "Wavelength (nm)", size = 20, color = "black" ) +
    scale_y_continuous(breaks = c(0,0.2, 0.4,0.6, 0.8, 1.0, 1.2), limits = c (0, 1.2)) +
   # scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
 scale_color_manual(values = Stock_ID, label = Stock_Label) +
  # coord_cartesian(ylim = c (0, 0.2)) +
 #ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+ 
 theme(
        axis.title = element_text(size = 20, color = "black"),
        axis.text = element_text(size = 15, color = "black"),
        # strip.background=element_rect(color="grey", fill = "grey"),
        # strip.background=element_rect(fill = "grey"),
        # legend.key.size = unit(1, 'cm'), #change legend key size
        # legend.key.height = unit(1, 'cm'), #change legend key height
        # legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title = element_text(size = 15),  #change legend title font size
   legend.text = element_text(size = 15)) + #change legend text font size
  labs(colour = "Strain")
